Short-term neuronal and synaptic plasticity act in synergy for deviance detection in spiking networks

### 2023-01-17 paper-1/manuscript.tex
Editing

Having established that the increased response to A in \dev{} trials was driven by lower thresholds before stimulation, we next turned to the cause of this reduction. A priori, since threshold adaptation is a direct reflection of activity, and since the response to target trials was larger in \dev{} than in \msc{}, the lower thresholds in \dev{} must have been caused by lower activity in non-target trials, i.e. lower responses to B in \dev{} than to B through E in \msc{}. Yet, since activity is modulated by thresholds as shown above, and since the dev sequence was random, meaning that thresholds before stimulation could carry no information about the upcoming stimulus, we might expect the lowered thresholds in \dev{} to yield not only higher target responses, but also higher non-target responses. To resolve this apparent paradox, we will turn to an analysis of the spatial arrangement of activity and adaptation.

>>>>

Having established that the increased response to A in \dev{} trials was driven by lower thresholds before stimulation, we next turned to the cause of this reduction. A priori, since threshold adaptation is a direct reflection of activity, and since the response to target trials was larger in \dev{} than in \msc{}, the lower thresholds in \dev{} must have been caused by lower activity in non-target trials, i.e. lower responses to B in \dev{} than to B through E in \msc{}. Yet, since activity is modulated by thresholds as shown above, and since the dev sequence was random, implying that $\T[dev]{A}{} \approx \T[dev]{B}{}$, we might expect the lowered thresholds in \dev{} to yield not only higher target responses, but also higher non-target responses. To resolve this apparent paradox, we will turn to an analysis of the spatial arrangement of activity and adaptation.
